---
---

```{r include=FALSE}
library(visreg)
knitr::opts_knit$set(aliases=c(h = 'fig.height', w = 'fig.width'))
knitr::opts_knit$set(global.par=TRUE)
knitr::opts_chunk$set(fig.path='img/options-')
```
```{r fake, echo=FALSE, results='hide'}
par(mar=c(5,5,0.75,0.5))
plot(1:10)
```

`visreg` tries to set up pleasant-looking default options, but everything can be tailored to user specifications.  For the plots below, we work from this general model:

```{r mod, h=5, w=5, cache=TRUE}
airquality$Heat <- cut(airquality$Temp, 3, labels=c("Cool", "Mild", "Hot"))
fit <- lm(Ozone ~ Solar.R + Wind + Heat, data=airquality)
```

# Turning on/off plot components

By default, `visreg` includes the fitted line, confidence bands, and partial residuals, but the residuals and the bands can be turned off:

```{r noband, h=5, w=5, cache=TRUE}
visreg(fit, "Wind", band=FALSE)
```

```{r nopartial, h=5, w=5, cache=TRUE}
visreg(fit, "Wind", partial=FALSE)
```

Note that by default, when you turn off partial residuals, visreg tries to display a rug so you can at least see where the observations are.  You can turn this off too:

```{r nopartial_norug, h=5, w=5, cache=TRUE}
visreg(fit, "Wind", partial=FALSE, rug=FALSE)
```

Finally, there is an option for displaying separate rugs for positive and negative residuals on the top and bottom axes, respectively, with `rug=2` (this is particularly useful for [logistic regression](glm.html)):

```{r rug2, h=5, w=5, cache=TRUE}
visreg(fit, "Wind", rug=2, partial=FALSE)
```

# Jittering

If there are many ties in a numeric variable `x`, jittering can be helpful way to avoid overplotting:

```{r nojit, h=5, w=5, cache=TRUE}
fit <- lm(Ozone ~ Solar.R + Wind + poly(Month, 2), data=airquality)
visreg(fit, "Month")
```

```{r jit, h=5, w=5, dependson="nojit", cache=TRUE}
visreg(fit, "Month", jitter=TRUE)
```

# Appearance of points, lines, and bands

Specifying `col='red'` won't work, because `visreg` can't know whether you're trying to change the color of the line, the band, or the points.  These options must be specified through separate parameters lists:

* `line.par`: Controls the appearance of the fitted line
* `fill.par`: Controls the appearance of the confidence band
* `points.par`: Controls the appearance of the partial residuals

Each of these can be abbreviated, as in the example below:

```{r aes, h=5, w=5, cache=TRUE}
visreg(fit, "Wind", line=list(col="red"),
                    fill=list(col="green"),
                    points=list(cex=1.5, pch=1))
```

# Generic plot options

Other options get passed along to `plot`, so any option that you could normally pass to `plot`, like `main`, will work fine.  Here's an example that includes a bunch of options like this:

```{r generic, h=5, w=5, cache=TRUE}
fit <- lm(log(Ozone) ~ Solar.R + Wind + Temp, data=airquality)
visreg(fit, "Wind", yaxt="n", main="Ozone is bad for you", bty="n", ylab="Ozone")
at <- seq(1.5, 5, 0.5)
lab <- round(exp(at), 1)
axis(2, at=at, lab=lab, las=1)
```

# Whitespace for factors

When `x` is a factor, the `whitespace` option controls the amount of whitespace in between the categories:

```{r whitespace, h=4, w=8, cache=TRUE}
fit <- lm(Ozone ~ Solar.R + Wind + Heat, data=airquality)
par(mfrow=c(1,2))
visreg(fit, "Heat", whitespace=.1)
visreg(fit, "Heat", whitespace=.5)
```

# Subsetting the plot

Occasionally, you might want to plot only a subset of the levels or observations; you can use `subset` to accomplish this:

```{r subset_1, h=4, w=7, cache=TRUE}
v <- visreg(fit, "Wind", by="Heat", plot=FALSE)
v1 <- subset(v, Heat %in% c("Cool", "Hot"))
plot(v1)
```

```{r subset_2, h=3, w=8}
v2 <- subset(v, Wind < 15)
plot(v2, layout=c(3,1))
```
