---
---

```{r include=FALSE}
library(visreg)
knitr::opts_knit$set(aliases=c(h = 'fig.height', w = 'fig.width'))
knitr::opts_knit$set(global.par=TRUE)
knitr::opts_chunk$set(fig.path='img/overlay-')
```
```{r fake, echo=FALSE, results='hide'}
par(mar=c(5,5,2,0.5))
plot(1:10)
```

The default [cross-sectional plot](cross.html) places the different cross-sections in separate panels.  Occasionally, it is more helpful to overlay the plots on top of one another to see more directly how they compare.  Using the same model as [before](cross.html):

```{r mod}
airquality$Heat <- cut(airquality$Temp, 3, labels=c("Cool", "Mild", "Hot"))
fit <- lm(Ozone ~ Solar.R + Wind * Heat, data=airquality)
```

We can specify `overlay=TRUE` to obtain a version of the plot in which all the images are overlaid:

```{r wind_heat, h=5, w=5, cache=TRUE}
visreg(fit, "Wind", by="Heat", overlay=TRUE)
```

```{r heat_wind, h=5, w=5, cache=TRUE}
visreg(fit, "Heat", by="Wind", overlay=TRUE)
```

The options described in [cross-sectional plots](cross.html) work in the same way here.  For example,

```{r breaks, h=5, w=5, cache=TRUE}
visreg(fit, "Heat", by="Wind", overlay=TRUE, breaks=c(6, 12))
```

In particular, the option `strip.names` is used in the same way for consistency, even though there are no actual strips in an overlay plot:

```{r names, h=5, w=5, cache=TRUE}
visreg(fit, "Wind", by="Heat", overlay=TRUE, strip.names=c("Cold", "Not so hot", "Really hot"))
```

Changing the appearance of lines, etc., is accomplished in a similar manner to [other `visreg` plots](options.html), although (1) you need to pass a vector to specify the appearance for differeny `by` levels and (2) you need to be sure that you're correctly matching the colors of lines, points, and bands:

```{r colors, h=5, w=5, cache=TRUE}
visreg(fit, "Wind", by="Heat", overlay=TRUE,
       line=list(col=c("#00C1C9", "#D63EFF", "#FF4E37"), lwd=1),
       fill=list(col=c("#00C1C980", "#D63EFF80", "#FF4E3780")),
       points=list(col=c("#00C1C9", "#D63EFF", "#FF4E37"), cex=1))
```

Note that you can still pass parameters as single elements (`cex=1`); these will apply to all levels of `by`.

For `gg` plots, the mechanism is different -- the returned plot can be modified with calls to `scale_xxx_manual()`:

```{r gg_colors, h=5, w=5, cache=TRUE, message=FALSE, warning=FALSE}
library(ggplot2)
visreg(fit, "Wind", by="Heat", overlay=TRUE, gg=TRUE) +
  scale_color_manual(values=c("#00C1C9", "#D63EFF", "#FF4E37")) +
  scale_fill_manual(values=c("#00C1C980", "#D63EFF80", "#FF4E3780"))
```
