---
title: Cross-sectional plots
---

```{r include=FALSE}
library(visreg)
library(ggplot2)
knitr::opts_knit$set(aliases=c(h = 'fig.height', w = 'fig.width'))
knitr::opts_chunk$set(comment='#', collapse=TRUE, cache=FALSE, tidy=FALSE)
knitr::knit_hooks$set(small.mar = function(before, options, envir) {
  if (before) par(mar = c(4, 4, .1, .1))
})
```

As was the case with [nonlinear terms](trans.html), the relationship between `x` and `y` in a model with interactions also (typically) depends on multiple coefficients and thus, a visual summary tends to be much more readily understood than a numeric one.

For models with interactions, we must simultaneously visualize the effect of two explanatory variables.  The `visreg` package offers two methods for doing so; this page describes what we call *cross-sectional plots*, which plot one-dimensional relationships between the response and one predictor for several values of another predictor, either in separate panels or [overlaid on top of one another](overlay.html).  The package also provides methods for constructing [*surface plots*](surface.html), which attempt to provide a picture of the regression surface over both dimensions simultaneously.

Let's fit a model that involves an interaction between a continuous term and a categorical term:

```{r}
airquality$Heat <- cut(airquality$Temp, 3, labels=c("Cool", "Mild", "Hot"))
fit <- lm(Ozone ~ Solar.R + Wind * Heat, data=airquality)
```

We can then use `visreg` to see how the effect of wind on ozone differs depending on the temperature:

```{r, h=4, w=9, out.width='100%'}
visreg(fit, "Wind", by="Heat")
```

Or alternatively, see how the effect of temperature depends on the wind level:

```{r, h=4, w=9, out.width='100%'}
visreg(fit, "Heat", by="Wind")
```

Note that, since `Wind` is a continuous variable, the panels above are somewhat arbitrary.  By default, `visreg` sets up three panels using the 10th, 50th, and 90th percentiles, but [the user can change both the number and the location of these break points](#opt).

In all of these plots, note that each partial residuals appears exactly once in the plot, in the panel it is closest to.

<a class="anchor" id="opt"></a>

# Options

For a numeric `by` variable, the `breaks` argument controls the values at which the cross-sections are taken. By default, cross-sections are taken at three quantiles (10th, 50th, and 90th), but a larger number can be specified:

```{r, h=3.5, w=12, out.width='100%'}
visreg(fit, "Heat", by="Wind", breaks=4)
```

If `breaks` is a vector of numbers, it specifies the values at which the cross-sections are to be taken:

```{r, h=4, w=9, out.width='100%'}
visreg(fit, "Heat", by="Wind", breaks=c(seq(5, 15, 5)))
```

# Graphical options

Plots are built with `ggplot2`, and the returned object has class `gg`, so its appearance can be changed via the usual `ggplot2` components, such as themes:

```{r, h=4, w=9, out.width='100%'}
visreg(fit, "Wind", by="Heat") + theme_bw()
```

The appearance of points, lines, and bands is set with the `line`, `fill`, and `points` arguments, [as described here](options.html):

```{r, h=4, w=9, out.width='100%'}
visreg(fit, "Wind", by="Heat", fill=list(fill="#008DFF33"))
```

`visreg` sets up the facet strips internally via the `strip.names` option:

```{r, h=4, w=9, out.width='100%'}
visreg(fit, "Wind", by="Heat", strip.names=TRUE)
```

You can also explicitly specify the labels for each strip:

```{r, h=4, w=9, out.width='100%'}
visreg(fit, "Wind", by="Heat", strip.names=c("Cold days", "Mild days", "Hot days"))
```

Other aspects of faceting, such as the number of rows/columns, can be changed by adding a new `facet_wrap()` (or `facet_grid()`) to the returned plot:

```{r, h=3.5, w=12, out.width='100%'}
visreg(fit, "Heat", by="Wind", breaks=4) + facet_wrap(~Wind, nrow=1)
```
