---
title: Cross-sectional plots
---

```{r}
#| include: false
library(visreg)
library(ggplot2)
theme_set(theme_minimal())
knitr::opts_chunk$set(fig.asp = 1 / 1.618)
```

As was the case with [nonlinear terms](trans.html), the relationship between `x` and `y` in a model with interactions also (typically) depends on multiple coefficients and thus, a visual summary tends to be much more readily understood than a numeric one.

For models with interactions, we must simultaneously visualize the effect of two explanatory variables.  The `visreg` package offers two methods for doing so; this page describes what we call *cross-sectional plots*, which plot one-dimensional relationships between the response and one predictor for several values of another predictor, either in separate panels or [overlaid on top of one another](overlay.html).  The package also provides methods for constructing [*surface plots*](surface.html), which attempt to provide a picture of the regression surface over both dimensions simultaneously.

Let's fit a model that involves an interaction between a continuous term and a categorical term:

```{r}
airquality$Heat <- cut(airquality$Temp, 3, labels = c("Cool", "Mild", "Hot"))
fit <- lm(Ozone ~ Solar.R + Wind * Heat, data = airquality)
```

We can then use `visreg` to see how the effect of wind on ozone differs depending on the temperature:

```{r}
#| out.width: 100%
#| fig-asp: 0.34
visreg(fit, "Wind", by = "Heat")
```

Or alternatively, see how the effect of temperature depends on the wind level:

```{r}
#| out.width: 100%
#| fig-asp: 0.34
visreg(fit, "Heat", by = "Wind")
```

Note that, since `Wind` is a continuous variable, the panels above are somewhat arbitrary.  By default, `visreg` sets up three panels using the 10th, 50th, and 90th percentiles, but [the user can change both the number and the location of these break points](#opt).

In all of these plots, note that each partial residuals appears exactly once in the plot, in the panel it is closest to.

# Options

For a numeric `by` variable, the `breaks` argument controls the values at which the cross-sections are taken. By default, cross-sections are taken at three quantiles (10th, 50th, and 90th), but a larger number can be specified:

```{r}
#| out.width: 100%
#| fig-asp: 0.25
visreg(fit, "Heat", by = "Wind", breaks = 4)
```

If `breaks` is a vector of numbers, it specifies the values at which the cross-sections are to be taken:

```{r}
#| out.width: 100%
#| fig-asp: 0.34
visreg(fit, "Heat", by = "Wind", breaks = c(seq(5, 15, 5)))
```

# Strip names

`visreg` sets up the facet strips internally via the `strip_names` option:

```{r}
#| out.width: 100%
#| fig-asp: 0.34
visreg(fit, "Wind", by = "Heat", strip_names = TRUE)
```

You can also explicitly specify the labels for each strip:

```{r}
#| out.width: 100%
#| fig-asp: 0.34
visreg(
  fit,
  "Wind",
  by = "Heat",
  strip_names = c("Cold days", "Mild days", "Hot days")
)
```

Other aspects of faceting, such as the number of rows/columns, can be changed by adding a new `facet_wrap()` (or `facet_grid()`) to the returned plot:

```{r}
#| out.width: 100%
#| fig-asp: 0.5
visreg(fit, "Heat", by = "Wind", breaks = 4) + facet_wrap(~Wind, nrow = 2)
```
