---
title: Frequently asked questions
---

```{r}
#| include: false
library(visreg)
library(ggplot2)
theme_set(theme_minimal())
knitr::opts_chunk$set(fig.asp = 1 / 1.618)
```

This page contains miscellaneous questions that I have been asked about visreg, with answers posted here so that others can read them too.

# Q: In `visreg2d`, is it possible to superimpose data points onto the plot?

Yes; `visreg2d()` renders its surface with `ggplot2`, so you can just add a layer:

```{r}
fit <- lm(
  Ozone ~ Solar.R +
    Wind +
    Temp +
    I(Wind^2) +
    I(Temp^2) +
    I(Wind * Temp) +
    I(Wind * Temp^2) +
    I(Temp * Wind^2) +
    I(Temp^2 * Wind^2),
  data = airquality
)
visreg2d(fit, x = "Wind", y = "Temp") +
  geom_point(
    aes(Wind, Temp),
    data = subset(airquality, !is.na(Ozone)),
    col = "gray50"
  )
```

# Q: Does `visreg` work with `gamm` (mgcv) or `gamm4` objects?

Yes, although it takes a minor workaround since these objects have an unusual structure.  First, let's simulate some data and fit a model (I'm just using a `tibble` here for convenience, it isn't relevant to the question):

```{r}
#| message: false
library(mgcv)
library(tibble)
n <- 20
dat <- tibble(
  ID = factor(rep(LETTERS[1:n], each = 5)),
  x = rnorm(n * 5),
  lp = rnorm(n)[as.numeric(ID)] + x^2 - 1,
  p = binomial()$linkinv(lp),
  y = rbinom(n * 5, 1, p)
)
fit <- gamm(y ~ s(x), data = dat, dist = "binomial", random = list(ID = ~1))
```

Now, `fit$gam` does not include the call (i.e., `fit$gam$call` is `NULL`), which means `visreg` won't be able to find the data:

```{r}
#| error: true
visreg(fit$gam, "x")
```

So you have to include it manually:

```{r}
fit$gam$data <- dat
visreg(fit$gam, "x")
```

# Q: I'm getting the following error message: `Error in UseMethod("family") : no applicable method for 'family' applied to an object of class XXXX`.

When you specify `scale='response'`, you're telling `visreg` to automatically find the transformation mapping the linear predictor to the scale of the response.  It can only do that if the fitted model object provides that transformation through the `family()` method.  Many R models (e.g., `glm`) do this, but some (e.g., the `glmmADMB` package, `gamm` from the `mgcv` package) don't.  If you're working with one of these models, you'll have to supply that transformation yourself.  For example, with the model from the previous question, this code fails:

```{r}
#| error: true
visreg(fit$gam, "x", scale = "response")
```

Since this is a binomial model with a logistic link, `binomial()$linkinv` provides the inverse transformation:

```{r}
visreg(fit$gam, "x", trans = binomial()$linkinv) + ylab("Probability")
```

# Q: Can I have the response variable on the horizontal axis instead of the vertical axis?

You can achieve this via `ggplot2::coord_flip`:

```{r}
fit <- lm(Ozone ~ Solar.R + Wind + Temp, data = airquality)
visreg(fit, "Wind") + coord_flip()
```
