---
title: Migrating to visreg 3.0
---

```{r}
#| echo: false
library(visreg)
ggplot2::theme_set(ggplot2::theme_minimal())
```

Version 3.0 of **visreg** is a breaking release. This article explains what changed, why, and how
to update your code. If you'd rather not update your code right now, see [Keeping the old
behavior](#keeping-the-old-behavior) below for how to keep using the pre-3.0 version.

## What changed, and why

**visreg** is old enough that it accumulated three separate plotting backends over the years:
base R graphics, `lattice`, and (added later, on top of the other two) `ggplot2`. Keeping all three
in sync as features were added became increasingly difficult, and most users only ever used the
`ggplot2` output anyway (via `gg = TRUE`). In 3.0, the base R and lattice plotting code has been
removed entirely: `plot.visreg()` now always builds and returns a `ggplot2` object, which you can
further modify with `+`, just as you would any other `ggplot2` plot. The `gg` argument is gone
because there is no longer a choice to make.

At the same time, the package's internal and user-facing naming was inconsistent — a mix of
`camelCase`, `dotted.names`, and `snake_case` left over from different eras of the codebase. 3.0
standardizes everything to `snake_case`. Most of this was internal and invisible to users, but a
handful of user-facing argument names changed as a result (see the table below). A few arguments
that only made sense for the old lattice/base-R backends (panel spacing, legend toggling) have been
removed, since `ggplot2` handles these automatically. `type = "effect"`, a deprecated alias for
`type = "contrast"` that had been printing a warning for years, has also been removed for good.

Separately, `visreg()` is now stricter about a common source of misleading plots: if you plot the
main effect of a variable that participates in an interaction, without using `by` or `cond` to
address the interaction, `visreg` now always warns you (previously this only happened in some
cases). This isn't a rename, but it's a behavior change worth knowing about if you see new warnings
after upgrading.

## Renamed and removed arguments

| Old (≤ 2.8.1) | New (≥ 3.0) | Where | Notes |
| --- | --- | --- | --- |
| `gg` | *(removed)* | `plot.visreg()` | Plots are always `ggplot2` now; there's nothing to toggle. |
| `line.par` | `line` | `plot.visreg()` | |
| `fill.par` | `fill` | `plot.visreg()` | |
| `points.par` | `points` | `plot.visreg()` | |
| `print.cond` | `print_cond` | `plot.visreg()` | |
| `strip.names` | `strip_names` | `plot.visreg()` | |
| `legend` | *(removed)* | `plot.visreg()` | `ggplot2` draws a legend automatically when one is needed; suppress it with `+ ggplot2::theme(legend.position = "none")`. |
| `whitespace` | *(removed)* | `plot.visreg()` | Controlled panel spacing in the old lattice backend; use standard `ggplot2`/`facet_grid()` mechanisms if you need to adjust spacing. |
| `xtrans` | *(removed)* | `visreg()` | |
| `type = "effect"` | `type = "contrast"` | `visreg()`, `visreg2d()` | The deprecated alias has been fully removed; `contrast` is the only spelling now. |
| `visregList()` | `visreg_list()` | top-level function | The function and the S3 class it returns (`"visregList"` → `"visreg_list"`) were both renamed. |

If you were passing any of the old dotted/camelCase names positionally rather than by name, that
will still work — only the names themselves changed, not the argument order.

## Renamed columns in the returned object

If your code reaches into the object returned by `visreg()` directly (rather than just plotting
it), note that the columns of the `fit` and `res` data frames were also renamed to `snake_case`:

| Old | New |
| --- | --- |
| `$fit$visregFit` | `$fit$visreg_fit` |
| `$fit$visregLwr` | `$fit$visreg_lwr` |
| `$fit$visregUpr` | `$fit$visreg_upr` |
| `$res$visregRes` | `$res$visreg_res` |
| `$res$visregPos` | `$res$visreg_pos` |

For example:

```{r}
fit <- lm(Ozone ~ Solar.R + Wind + Temp, data = airquality)
v <- visreg(fit, "Wind", plot = FALSE)
head(v$fit[, c("Wind", "visreg_fit", "visreg_lwr", "visreg_upr")])
```

## A worked example

Old (2.8.1 and earlier) code that customized the appearance of a plot might have looked like this:

```r
visreg(fit, "Wind", gg = TRUE,
  line.par = list(col = "red"),
  fill.par = list(fill = "green"),
  points.par = list(cex = 2, pch = 1)
)
```

The 3.0 equivalent drops `gg = TRUE` (no longer needed) and renames the three styling arguments:

```{r}
visreg(fit, "Wind",
  line = list(color = "red"),
  fill = list(fill = "green"),
  points = list(size = 2, shape = 1)
)
```

Note that the *values* passed to `line`/`fill`/`points` are `ggplot2` aesthetics (`color`, `size`,
`shape`, ...), not base R `par()` names (`col`, `cex`, `pch`) --- this was already true whenever
`gg = TRUE` was used pre-3.0, so it should look familiar if you were already using the `ggplot2`
backend. See [Graphical options](options) for details.

## Still in progress

3.0 is still being finished, and this article will be updated as the remaining pieces land:

- **Mixed models.** Prediction and standard-error handling for `lme4`/`nlme`/`glmmTMB` models is
  being reworked, and the [mixed models article](mixed) hasn't been updated to reflect the new
  `predict` argument to `visreg()` yet (an escape hatch for passing arguments like `re.form` through
  to the model's own `predict()` method). Don't be surprised if this area continues to change.
- **`visreg2d()`.** The 2D surface-plotting functions are being rethought and, unlike the rest of
  the package, still use the old base R plotting code and naming conventions in places. They are
  not yet part of the ggplot2-only, snake_case cleanup described above.

## Keeping the old behavior

If you're not ready to update your code, you don't have to: the last CRAN release before these
changes, version 2.8.1, remains available and can be installed alongside or instead of the current
version:

```r
remotes::install_version("visreg", "2.8.1")
```
