---
title: Mixed models
---

```{r}
#| include: false
library(visreg)
library(ggplot2)
theme_set(theme_minimal())
knitr::opts_chunk$set(fig.asp = 1 / 1.618)
```

`visreg` can be used to visualize mixed models, although whether you get confidence intervals or not depends on the package you're using. I can't provide a comprehensive listing of all mixed model packages, but:

- `lme4`: As of 1.1-27, `predict.merMod()` supports `se.fit=TRUE`, so `visreg` provides confidence bands. The rest of the article illustrates how to use `visreg()` with `lme4`.
- `nlme`: A of 3.1.169, `predict.lme()` does not support `se.fit`. Since it doesn't provide standard errors, `visreg()` cannot produce confidence bands (except for [contrast plots](contrast.html)).

To illustrate, we will work with this random-intercept, random-slope model of data from a study
involving the protein content of cows' milk in the weeks following calving:

```{r}
#| message: false
library(lme4)
data(Milk, package = "nlme")
ctrl <- lmerControl(optCtrl = list(xtol_rel = 1e-6)) # Warning otherwise
fit <- lmer(protein ~ Diet + Time + (Time | Cow), Milk, control = ctrl)
```

# Population-level effects (the default)

By default, `visreg` predicts with `re.form=NA`: the random effects are ignored altogether, and
the plot shows the fixed-effect (population-average) relationship, with a confidence band
reflecting uncertainty about the fixed effects only. No extra arguments are needed for this ---
it's what you get by calling `visreg()` normally:

```{r}
visreg(fit, "Diet") + ylab("Protein")
```

This is the right choice when you want to describe the typical cow, and it's the plot most people
want most of the time.

# Conditioning on the estimated random effects

Passing `predict = list(re.form = NULL)` tells `lme4` to condition on the estimated (BLUP) random
effects for a specific cow. Combined with `by`, this lets you plot cow-specific curves --- the estimated relationship between protein and time,
separately for each cow. For the sake of space, we subset the plot to 8 cows rather than all 79;
this can be done by returning, then subsetting, the raw `visreg` object prior to plotting.

```{r}
#| out.width: 100%
#| fig-width: 9
#| fig-asp: 0.2
sub_cow <- sample(levels(Milk$Cow), 8)
visreg(fit, "Time", by = "Cow", predict = list(re.form = NULL), plot = FALSE) |>
  subset(Cow %in% sub_cow) |>
  plot() +
  ylab("Protein")
```

Each cow's curve now has its own confidence band, but it's worth being clear about what these
bands represent: they reflect the precision with which *that cow's own trajectory* is estimated,
given its random effects, and are a different quantity than the population-level band above, which
reflects uncertainty about the fixed effects for a typical cow.

# Conditioning on some, but not all, random effects

When a model has more than one grouping factor, `re.form` can also be a formula naming just the
grouping factor(s) you want to condition on, letting you marginalize over the rest. This isn't an
option for the milk yield model above, which has only one grouping factor (`Cow`), so let's simulate a small artificial example involving patients seen at different clinics, and both patients and clinics
have their own random intercepts:

```{r}
set.seed(1)
n_clinic <- 15
n_patient <- 20
n <- 300
clinic <- factor(sample(1:n_clinic, n, replace = TRUE))
patient <- factor(sample(1:n_patient, n, replace = TRUE))
severity <- runif(n)
b_clinic <- rnorm(n_clinic, sd = 0.5)
b_patient <- rnorm(n_patient, sd = 1)
outcome <- 2 +
  1.5 * severity +
  b_clinic[clinic] +
  b_patient[patient] +
  rnorm(n, sd = 0.3)
dat <- data.frame(outcome, severity, clinic, patient)
fit2 <- lmer(outcome ~ severity + (1 | patient) + (1 | clinic), data = dat)
```

Conditioning on clinic random effects while marginalizing over patient random effects:

```{r}
visreg(
  fit2,
  "severity",
  predict = list(re.form = ~ (1 | clinic)),
  cond = list(clinic = levels(clinic)[1])
) +
  ylab("Outcome")
```

This differs from both the fully marginal plot (`re.form=NA`, the default) and the fully
conditional one (`re.form=NULL`, conditioning on both clinic and patient): it reflects the
uncertainty coming from random patients, but is specific to the clinic being examined.
