---
title: Multiple outcomes
---

```{r}
#| include: false
library(visreg)
library(ggplot2)
theme_set(theme_minimal())
knitr::opts_knit$set(aliases = c(h = "fig.height", w = "fig.width"))
```

Multiple `visreg` objects can be bundled together in an object of class `visreg_list`. For example, suppose we fit a multinomial regression model using the `nnet` package:

```{r}
#| message: false
#| output: false
library(nnet)
airquality$Heat <- cut(airquality$Temp, 3, labels = c("Cool", "Mild", "Hot"))
fit <- multinom(Heat ~ Wind + Ozone, airquality)
```

By default, `visreg(fit, "Ozone")` would create three separate plots, one for each level of the outcome, `Heat`.  By specifying `collapse=TRUE`, we collapse the list down to a single `visreg` object which can be plotted using the [methods](cross.html) [described](overlay.html) [here](surface.html).  For example:

```{r}
#| message: false
visreg(fit, "Ozone", collapse = TRUE, overlay = TRUE, partial = FALSE) +
  coord_cartesian(ylim = 0:1) +
  ylab("Probability")
```

Another example is quantile regression using the `quantreg` package.  Here, there is only one outcome, but we could be interested in modeling several different quantiles.  The `collapse` option is used similarly here:

```{r}
#| message: false
library(quantreg)
fit <- rq(Ozone ~ Wind + Temp, tau = c(0.25, 0.5, 0.75), data = airquality)
v <- visreg(fit, "Wind", overlay = TRUE, collapse = TRUE)
```

NOTE: `quantreg` does not return standand errors if you specify multiple quantiles of interest.  To obtain them, you must construct the `visreg_list` manually:

```{r}
#| out.width: 100%
fit1 <- rq(Ozone ~ Wind + Temp, tau = 0.25, data = airquality)
fit2 <- rq(Ozone ~ Wind + Temp, tau = 0.5, data = airquality)
fit3 <- rq(Ozone ~ Wind + Temp, tau = 0.75, data = airquality)
v <- visreg_list(visreg(fit1, "Wind", plot = FALSE),
  visreg(fit2, "Wind", plot = FALSE),
  visreg(fit3, "Wind", plot = FALSE),
  labels = c("25%", "50%", "75%"), collapse = TRUE
)
plot(v) + ylab("Ozone")
```

Notice the use of the `labels` argument to label the elements of the list.
