---
title: Multiple outcomes
---

```{r include=FALSE}
library(visreg)
knitr::opts_knit$set(aliases=c(h = 'fig.height', w = 'fig.width'))
knitr::opts_chunk$set(comment='#', collapse=TRUE, cache=FALSE, tidy=FALSE)
knitr::knit_hooks$set(small.mar = function(before, options, envir) {
  if (before) par(mar = c(4, 4, .1, .1))
})
```

Multiple `visreg` objects can be bundled together in an object of class `visregList`; for example, when you submit `visreg(fit)`, you get a `visregList`, one `visreg` object for each predictor in the model.  `visregList`s can also be used for handling models with multiple outcomes.

For example, suppose we fit a multinomial regression model using the `nnet` package:

```{r, message=FALSE, results='hide'}
library(nnet)
airquality$Heat <- cut(airquality$Temp,3,labels=c("Cool","Mild","Hot"))
fit <- multinom(Heat ~ Wind + Ozone, airquality)
```

By default, `visreg(fit, "Ozone")` would create three separate plots, one for each level of the outcome, `Heat`.  By specifying `collapse=TRUE`, we collapse the list down to a single `visreg` object which can be plotted using the [methods](cross.html) [described](overlay.html) [here](surface.html).  For example:

```{r, message=FALSE, h=5, w=5}
visreg(fit, "Ozone", collapse=TRUE, overlay=TRUE, ylab="Probability",
       ylim=c(0,1), partial=FALSE, rug=2)
```

Another example is quantile regression using the `quantreg` package.  Here, there is only one outcome, but we could be interested in modeling several different quantiles.  The `collapse` option is used similarly here:

```{r, message=FALSE, h=5, w=5}
library(quantreg)
fit <- rq(Ozone ~ Wind + Temp, tau=c(.25, .5, .75), data=airquality)
v <- visreg(fit, "Wind", overlay=TRUE, collapse=TRUE)
```

NOTE: `quantreg` does not return standand errors if you specify multiple quantiles of interest.  To obtain them, you must construct the `visregList` manually:

```{r, h=3, w=9, out.width='100%'}
fit1 <- rq(Ozone ~ Wind + Temp, tau=.25, data=airquality)
fit2 <- rq(Ozone ~ Wind + Temp, tau=.5, data=airquality)
fit3 <- rq(Ozone ~ Wind + Temp, tau=.75, data=airquality)
v <- visregList(visreg(fit1, "Wind", plot=FALSE),
                visreg(fit2, "Wind", plot=FALSE),
                visreg(fit3, "Wind", plot=FALSE),
                labels=c("25%", "50%", "75%"), collapse=TRUE)
plot(v, ylab="Ozone", gg=TRUE)
```

Notice the use of the `labels` argument to label the elements of the list.
