---
title: Graphical options
---

```{r}
#| include: false
library(visreg)
library(ggplot2)
theme_set(theme_minimal())
knitr::opts_chunk$set(fig.asp = 1 / 1.618)
```

`visreg` tries to set up pleasant-looking default options, but everything can be tailored to user specifications. For the plots below, we work from this general model:

```{r}
airquality$Heat <- cut(airquality$Temp, 3, labels = c("Cool", "Mild", "Hot"))
fit <- lm(Ozone ~ Solar.R + Wind + Heat, data = airquality)
```

# Turning on/off plot components

By default, `visreg` includes the fitted line, confidence bands, and partial residuals, but the residuals and the bands can be turned off:

```{r}
visreg(fit, "Wind", band = FALSE)
```

```{r}
visreg(fit, "Wind", partial = FALSE)
```

```{r}
visreg(fit, "Wind", partial = FALSE, rug = TRUE)
```

# Jittering

If there are many ties in a numeric variable `x`, jittering can be helpful way to avoid overplotting. Compare the following two plots:

```{r}
#| fig-width: 4
#| out.width: 100%
#| layout-ncol: 2
month_fit <- lm(Ozone ~ Solar.R + Wind + poly(Month, 2), data = airquality)
visreg(month_fit, "Month")
visreg(month_fit, "Month", jitter = TRUE)
```

# Appearance of points, lines, and bands

Specifying `col='red'` won't work, because `visreg` can't know whether you're trying to change the color of the line, the band, or the points. These options must be specified through separate parameter lists:

* `line`: Controls the appearance of the fitted line
* `fill`: Controls the appearance of the confidence band
* `points`: Controls the appearance of the partial residuals

Each of these is passed along to the underlying `ggplot2` geom (`geom_line`/`geom_ribbon`/`geom_point` for a continuous `x`, or `geom_errorbar`/`geom_tile`/`geom_jitter` for a factor `x`), so any parameter that geom accepts can be specified:

```{r}
visreg(
  fit,
  "Wind",
  line = list(color = "red"),
  fill = list(fill = "green"),
  points = list(size = 2, shape = 1)
)
```

# Generic plot options

`visreg` returns a `gg` object, so its appearance can be customized just like any other `ggplot2` plot, by adding further components. Here's an example that adds a title and re-labels the (log-transformed) y-axis:

```{r}
fit <- lm(log(Ozone) ~ Solar.R + Wind + Temp, data = airquality)
at <- seq(1.5, 5, 0.5)
visreg(fit, "Wind") +
  labs(title = "Ozone is bad for you", y = "Ozone") +
  scale_y_continuous(breaks = at, labels = round(exp(at), 1))
```

# Band width for factors

When `x` is a factor, the width of the confidence band (and its accompanying line) is controlled through the `fill`/`line` arguments' `width` parameter:

```{r}
#| fig-width: 4
#| out.width: 100%
#| layout-ncol: 2
fit <- lm(Ozone ~ Solar.R + Wind + Heat, data = airquality)
visreg(fit, "Heat", line = list(width = 0.98), fill = list(width = 0.98))
visreg(fit, "Heat", line = list(width = 0.1), fill = list(width = 0.1))
```

# Subsetting the plot

Occasionally, you might want to plot only a subset of the levels or observations; you can use `subset` to accomplish this:

```{r}
#| out.width: 100%
#| fig-asp: 0.5
v <- visreg(fit, "Wind", by = "Heat", plot = FALSE)
v1 <- subset(v, Heat %in% c("Cool", "Hot"))
plot(v1)
```

```{r}
#| out.width: 100%
#| fig-asp: 0.34
v2 <- subset(v, Wind < 15)
plot(v2)
```
