---
title: Graphical options
---

```{r include=FALSE}
library(visreg)
library(ggplot2)
knitr::opts_knit$set(aliases = c(h = "fig.height", w = "fig.width"))
knitr::opts_chunk$set(comment = "#", collapse = TRUE, cache = FALSE, tidy = FALSE)
knitr::knit_hooks$set(small.mar = function(before, options, envir) {
  if (before) par(mar = c(4, 4, .1, .1))
})
```

`visreg` tries to set up pleasant-looking default options, but everything can be tailored to user specifications.  For the plots below, we work from this general model:

```{r, h=5, w=5}
airquality$Heat <- cut(airquality$Temp, 3, labels = c("Cool", "Mild", "Hot"))
fit <- lm(Ozone ~ Solar.R + Wind + Heat, data = airquality)
```

# Turning on/off plot components

By default, `visreg` includes the fitted line, confidence bands, and partial residuals, but the residuals and the bands can be turned off:

```{r, h=5, w=5}
visreg(fit, "Wind", band = FALSE)
```

```{r, h=5, w=5}
visreg(fit, "Wind", partial = FALSE)
```

Note that by default, when you turn off partial residuals, visreg tries to display a rug so you can at least see where the observations are.  You can turn this off too:

```{r, h=5, w=5}
visreg(fit, "Wind", partial = FALSE, rug = FALSE)
```

Finally, there is an option for displaying separate rugs for positive and negative residuals on the top and bottom axes, respectively, with `rug=2` (this is particularly useful for [logistic regression](glm.html)):

```{r, h=5, w=5}
visreg(fit, "Wind", rug = 2, partial = FALSE)
```

# Jittering

If there are many ties in a numeric variable `x`, jittering can be helpful way to avoid overplotting:

```{r, h=5, w=5}
fit <- lm(Ozone ~ Solar.R + Wind + poly(Month, 2), data = airquality)
visreg(fit, "Month")
```

```{r, h=5, w=5, dependson="nojit"}
visreg(fit, "Month", jitter = TRUE)
```

# Appearance of points, lines, and bands

Specifying `col='red'` won't work, because `visreg` can't know whether you're trying to change the color of the line, the band, or the points.  These options must be specified through separate parameter lists:

* `line`: Controls the appearance of the fitted line
* `fill`: Controls the appearance of the confidence band
* `points`: Controls the appearance of the partial residuals

Each of these is passed along to the underlying `ggplot2` geom (`geom_line`/`geom_ribbon`/`geom_point` for a continuous `x`, or `geom_errorbar`/`geom_tile`/`geom_jitter` for a factor `x`), so any parameter that geom accepts can be specified:

```{r, h=5, w=5}
visreg(fit, "Wind",
  line = list(color = "red"),
  fill = list(fill = "green"),
  points = list(size = 1.5, shape = 1)
)
```

# Generic plot options

`visreg` returns a `gg` object, so its appearance can be customized just like any other `ggplot2` plot, by adding further components.  Here's an example that adds a title and re-labels the (log-transformed) y-axis:

```{r, h=5, w=5}
fit <- lm(log(Ozone) ~ Solar.R + Wind + Temp, data = airquality)
at <- seq(1.5, 5, 0.5)
visreg(fit, "Wind", ylab = "Ozone") +
  ggtitle("Ozone is bad for you") +
  scale_y_continuous(breaks = at, labels = round(exp(at), 1))
```

# Band width for factors

When `x` is a factor, the width of the confidence band (and its accompanying line) is controlled through the `fill`/`line` arguments' `width` parameter:

```{r, h=4, w=4}
fit <- lm(Ozone ~ Solar.R + Wind + Heat, data = airquality)
visreg(fit, "Heat", fill = list(width = .9))
```

```{r, h=4, w=4}
visreg(fit, "Heat", fill = list(width = .1))
```

# Subsetting the plot

Occasionally, you might want to plot only a subset of the levels or observations; you can use `subset` to accomplish this:

```{r, h=4, w=7}
v <- visreg(fit, "Wind", by = "Heat", plot = FALSE)
v1 <- subset(v, Heat %in% c("Cool", "Hot"))
plot(v1)
```

```{r, h=3, w=8}
v2 <- subset(v, Wind < 15)
plot(v2)
```
