---
title: Overlay plots
---

```{r}
#| include: false
library(visreg)
library(ggplot2)
theme_set(theme_minimal())
knitr::opts_chunk$set(comment = "#", collapse = TRUE, cache = FALSE, tidy = FALSE, fig.asp = 1 / 1.618)
```

The default [cross-sectional plot](cross.html) places the different cross-sections in separate panels.  Occasionally, it is more helpful to overlay the plots on top of one another to see more directly how they compare.  Using the same model as [before](cross.html):

```{r}
airquality$Heat <- cut(airquality$Temp, 3, labels = c("Cool", "Mild", "Hot"))
fit <- lm(Ozone ~ Solar.R + Wind * Heat, data = airquality)
```

We can specify `overlay=TRUE` to obtain a version of the plot in which all the images are overlaid:

```{r}
visreg(fit, "Wind", by = "Heat", overlay = TRUE)
```

```{r}
visreg(fit, "Heat", by = "Wind", overlay = TRUE)
```

The options described in [cross-sectional plots](cross.html) work in the same way here.  For example,

```{r}
visreg(fit, "Heat", by = "Wind", overlay = TRUE, breaks = c(6, 12))
```

In particular, the option `strip_names` is used in the same way for consistency, even though there are no actual strips in an overlay plot:

```{r}
visreg(fit, "Wind", by = "Heat", overlay = TRUE, strip_names = c("Cold", "Not so hot", "Really hot"))
```

Changing the appearance of lines and points that are common to all levels of `by` is accomplished in the same manner as [other `visreg` plots](options.html):

```{r}
visreg(fit, "Wind", by = "Heat", overlay = TRUE, line = list(linewidth = 1))
```

Since the colors of the lines, points, and bands in an overlay plot are mapped to the levels of `by`, changing them level-by-level is done the usual `ggplot2` way, by adding a scale to the returned plot:

```{r}
#| message: false
visreg(fit, "Wind", by = "Heat", overlay = TRUE) +
  scale_color_manual(values = c("#00C1C9", "#D63EFF", "#FF4E37")) +
  scale_fill_manual(values = c("#00C1C980", "#D63EFF80", "#FF4E3780"))
```
