---
title: Surface plots
---

```{r}
#| include: false
library(visreg)
library(ggplot2)
theme_set(theme_minimal())
knitr::opts_knit$set(aliases = c(h = "fig.height", w = "fig.width"))
```

Suppose we have a model with a complicated interaction between two continuous variables:

```{r}
#| message: false
library(splines)
fit <- lm(Ozone ~ Solar.R + ns(Wind, df = 2) * ns(Temp, df = 2), data = airquality)
```

We might wish to visualize how ozone depends on wind and temperature as a continuous regression surface. `visreg2d` provides two main options for this, raster plots and perspective plots.

# Raster plots

The default is to provide a raster plot, built with `ggplot2`:

```{r}
visreg2d(fit, "Wind", "Temp")
```

Here, wind and temperature are laid out on a two-dimensional grid, and colors are used to represent the level of ozone. A legend is provided to the right. Because the result is a `ggplot2` object, you can further customize it as you would any other `ggplot2` plot; for example, if we want different colors,

```{r}
visreg2d(fit, "Wind", "Temp", color = c("black", "white", "purple"))
```

# Perspective plots

The other option provided by `visreg2d` is to represent the surface as a three-dimensional image. This can be done in a static manner by computing the surface with `plot = FALSE` and passing the result to `persp()`:

```{r}
visreg2d(fit, "Wind", "Temp", plot = FALSE) |> persp()
```

Or dynamically using `rgl::persp3d()`. For this, you will need to install the `rgl` package first.

```{r}
#| eval: false
visreg2d(fit, "Wind", "Temp", plot = FALSE) |> rgl::persp3d()
```

```{r}
#| echo: false
#| warning: false
#| message: false
library(rgl)
options(rgl.useNULL = TRUE)
visreg2d(fit, "Wind", "Temp", plot = FALSE) |> rgl::persp3d()
rgl::rglwidget()
```
