---
title: Surface plots
---

```{r include=FALSE}
library(visreg)
knitr::opts_knit$set(aliases=c(h = 'fig.height', w = 'fig.width'))
knitr::opts_chunk$set(comment='#', collapse=TRUE, cache=FALSE, tidy=FALSE)
knitr::knit_hooks$set(small.mar = function(before, options, envir) {
  if (before) par(mar = c(4, 4, .1, .1))
})
```

Suppose we have a model with a complicated interaction between two continuous variables:

```{r, message=FALSE}
library(splines)
fit <- lm(Ozone ~ Solar.R +ns(Wind, df=2)*ns(Temp, df=2), data=airquality)
```

We might wish to visualize how ozone depends on wind and temperature as a continuous regression surface. `visreg2d` provides two main options for this, filled contour plots and perspective plots.

# Filled contour plots

The default is to provide a contoured image plot:

```{r, h=4, w=5}
visreg2d(fit, "Wind", "Temp")
```

Here, wind and temperature are laid out on a two-dimensional grid, and colors are used to represent the level of ozone.  A legend is provided to the left.  R's `filled.contour` function is used to generate the plot, so if you wish to change any options, you will need to look at `?filled.contour` to see the correct syntax.  For example, if we want different colors,

```{r, h=4, w=5}
visreg2d(fit, "Wind", "Temp", color.palette=colorRampPalette(c("black", "white", "purple")))
```

# Perspective plots

The other option provided by `visreg2d` is to represent the surface as a three-dimensional image.  This can be done in a static manner using `type="persp"`:

```{r, h=5, w=5}
visreg2d(fit, "Wind", "Temp", plot.type="persp")
```

Or dynamically using `type="rgl"`:

```{r eval=FALSE}
visreg2d(fit, "Wind", "Temp", plot.type="rgl")
```

```{=html}
<div class="container" style="width: 100%">
  <div class="row-fluid">
    <iframe class="span12" 
	    style="border: none; height: 484px; width: 100%"
	    src="rgl.html">
    </iframe>
  </div>
</div>
```

For the interactive `rgl` option, you will need to install the `rgl` package first.
