---
title: Cross-sectional plots
---

```{r include=FALSE}
library(visreg)
library(ggplot2)
knitr::opts_knit$set(aliases=c(h = 'fig.height', w = 'fig.width'))
knitr::opts_knit$set(global.par=TRUE)
knitr::opts_chunk$set(fig.path='img/cross-')
```
```{r fake, echo=FALSE, results='hide'}
par(mar=c(5,5,0.5,0.5))
plot(1:10)
```

As was the case with [nonlinear terms](trans.html), the relationship between `x` and `y` in a model with interactions also (typically) depends on multiple coefficients and thus, a visual summary tends to be much more readily understood than a numeric one.

For models with interactions, we must simultaneously visualize the effect of two explanatory variables.  The `visreg` package offers two methods for doing so; this page describes what we call *cross-sectional plots*, which plot one-dimensional relationships between the response and one predictor for several values of another predictor, either in separate panels or [overlaid on top of one another](overlay.html).  The package also provides methods for constructing [*surface plots*](surface.html), which attempt to provide a picture of the regression surface over both dimensions simultaneously.

Let's fit a model that involves an interaction between a continuous term and a categorical term:

```{r mod}
airquality$Heat <- cut(airquality$Temp, 3, labels=c("Cool", "Mild", "Hot"))
fit <- lm(Ozone ~ Solar.R + Wind * Heat, data=airquality)
```

We can then use `visreg` to see how the effect of wind on ozone differs depending on the temperature:

```{r wind_heat, h=4, w=9, cache=TRUE}
visreg(fit, "Wind", by="Heat", layout=c(3,1))
```

Or alternatively, see how the effect of temperature depends on the wind level:

```{r heat_wind, h=4, w=9, cache=TRUE}
visreg(fit, "Heat", by="Wind", layout=c(3,1))
```

Note that, since `Wind` is a continuous variable, the panels above are somewhat arbitrary.  By default, `visreg` sets up three panels using the 10th, 50th, and 90th percentiles, but [the user can change both the number and the location of these break points](#opt).

By default, `visreg` uses the `lattice` package to lay out the panels.  Thus, in order to change the appearance of these sorts of plots, you may have to read the `lattice` documentation for the relevant options, such as `layout` in the above examples.  Alternatively, you can use [`ggplot2`](gg.html) as the graphics engine by specifying `gg=TRUE`:

```{r wind_heat_gg, h=4, w=9, cache=TRUE}
visreg(fit, "Wind", by="Heat", gg=TRUE)
```

```{r heat_wind_gg, h=4, w=9, cache=TRUE}
visreg(fit, "Heat", by="Wind", gg=TRUE)
```

In all of these plots, note that each partial residuals appears exactly once in the plot, in the panel it is closest to.

<a class="anchor" id="opt"></a>

# Options

For a numeric `by` variable, the `breaks` argument controls the values at which the cross-sections are taken. By default, cross-sections are taken at three quantiles (10th, 50th, and 90th), but a larger number can be specified:

```{r breaks, h=3.5, w=12, cache=TRUE}
visreg(fit, "Heat", by="Wind", breaks=4, layout=c(4,1))
```

If `breaks` is a vector of numbers, it specifies the values at which the cross-sections are to be taken:

```{r breaks_vec, h=4, w=9, cache=TRUE}
visreg(fit, "Heat", by="Wind", breaks=c(seq(5, 15, 5)), layout=c(3,1))
```

# Graphical options: `lattice`

As mentioned above, when using `lattice` as the graphics engine, the appearance of a plot can typically be changed by specifying the appropriate `lattice` option, which gets passed along by `visreg`.  One exception is the appearance of lines, points, and bands, which are specified [just as they are in base plots](options.html):

```{r lattice, h=4, w=9, cache=TRUE}
visreg(fit, "Wind", by="Heat", layout=c(3,1), fill.par=list(col="#008DFF33"))
```

Another exception is the `strip` option; `visreg` sets up the strip internally, which interferes with the user passing the `strip` option along to `lattice`.  `visreg` does, however, explicitly provide the `strip.names` option:

```{r strip_true, h=4, w=9, cache=TRUE}
visreg(fit, "Wind", by="Heat", layout=c(3,1), strip.names=TRUE)
```

You can also explicitly specify the labels for each strip:

```{r strip_labs, h=4, w=9, cache=TRUE}
visreg(fit, "Wind", by="Heat", layout=c(3,1), strip.names=c("Cold days", "Mild days", "Hot days"))
```

Other aspects of the strip's appearance, such as the background color, can be set with calls to the `lattice` package's `trellis.par.set`:

```{r trellis_bkg, h=4, w=9, cache=TRUE}
trellis.par.set(strip.background=list(col="gray90"))
visreg(fit, "Wind", by="Heat", layout=c(3,1))
```

# Graphical options: `ggplot2`

As discussed on the [`ggplot2`](gg.html) page, most `ggplot2` options are specified via additional components to the plot, such as:

```{r gg_theme, h=4, w=9, cache=TRUE}
visreg(fit, "Wind", by="Heat", gg=TRUE) + theme_bw()
```

The exception, again, is the appearance of points/lines/bands, which are specified with the usual `visreg` arguments:

```{r gg_fill, h=4, w=9, cache=TRUE}
visreg(fit, "Wind", by="Heat", gg=TRUE, fill.par=list(fill="#008DFF33"))
```
